Efficient Selection of Time Series Shapelets

### 2024-04-22 Docs/paper/main.tex
Experimental evaluation general

\section{Experimental Evaluation}

>>>>

\section{Experimental Evaluation}
In this section we compare the running time and the accuracy of our two
approaches with the baselines, namely:
(1) Ultra fast shapelet transform, which randomly select shapelets, evaluate
selects the ones with the highest rank. (2) Learning shapelets. (3) Fast them,
and Shapelet Selection (FSS).
